Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-08-31 analysis/presentation/sim_survey_presentation.Rmd
Add interpretations of the results to the presentation and start conclusions

---
title: "Using simulation to optimize the sampling design of fisheries-independent trawl surveys"
author: "Paul M. Regular & Fran Mowbray"
date: "September 6^th^, 2018"
output:
  ioslides_presentation:
    widescreen: true
    incremental: true
    logo: dfo_logo.png
    css: dfo_style.css
bibliography: references.bib
---

@@

- Split grid into $N_{div}$ divisions and $N_{strat}$ depth-based strata
- Set allocation defined by specifying set density, $D_{sets}$
- Binomial sampling was used to simulate catch:
    - $n_{a,y,s} \sim Bin(N_{a,y,s}, \frac{A_{trawl}}{A_{cell}} q_a )$
    - Accounts for trawl size relative to cell size, $\frac{A_{trawl}}{A_{cell}}$, and catchability, $q_a$ (controled using a logistic curve)

@@

<dev class = "left">
```{r}
plot_error_surface(sim) %>% tight_layout()
```
</dev>

@@

<dev class = "left">
```{r}
load("analysis/cod_sim_exports/2018-07-16_test/test_output.RData")
plot_age_strat_fan(sim, surveys = surveys$survey,
                   ages = 2:6, years = sim$years, select_by = "age",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>

@@

<dev class = "left">
```{r}
plot_error_surface(sim) %>% tight_layout()
```
</dev>

>>>>

---
title: "Using simulation to optimize the sampling design of fisheries-independent trawl surveys"
author: "Paul M. Regular & Fran Mowbray"
date: "September 6^th^, 2018"
output:
  ioslides_presentation:
    mathjax: local
    self_contained: false
    widescreen: true
    incremental: true
    logo: dfo_logo.png
    css: dfo_style.css
bibliography: references.bib
---

@@

- Split grid into $N_{div}$ divisions and $N_{strat}$ depth-based strata
- Set allocation defined by specifying set density, $D_{sets}$
- Binomial sampling was used to simulate catch:
    - $n_{a,y,s} \sim Bin(N_{a,y,s}, \frac{A_{trawl}}{A_{cell}} q_a )$
    - Accounts for trawl size relative to cell size, $\frac{A_{trawl}}{A_{cell}}$, and catchability, $q_a$ (controlled using a logistic curve)

@@

<dev class = "left">
```{r}
slide_font <- list(size = 14, color = rgb(121, 121, 121, maxColorValue = 255))
surface_font <- list(titlefont = slide_font, 
                     tickfont = slide_font)
surface_scene <- list(
  xaxis = surface_font,
  yaxis = surface_font,
  zaxis = surface_font
)
plot_error_surface(sim) %>% 
  tight_layout(scene = surface_scene,
               margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```
</dev>

@@

<dev class = "left">
```{r}
main_sim <- sim
load("analysis/cod_sim_exports/2018-07-16_test/test_output.RData")
plot_age_strat_fan(sim, surveys = surveys$survey,
                   ages = 2:6, years = sim$years, select_by = "age",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>

@@

<dev class = "left">
```{r}
plot_error_surface(sim) %>% 
  tight_layout(scene = surface_scene,
               margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```
</dev>

<br>

>- Increases in secondary sampling does little to improve estimates
>- Bias is negligible in this scenario

## Interpretation

Why is there bias? Why is extra sub-sampling ineffective or detrimental?

- With age-specific clustering, fish of different ages are not encountered with equal probability
    - A survey with few sets will be less likely to encounter groups in a tight cluster
        - Survey-level length / age distribution ∴ more likely to be incomplete 
            - Increasing length / age sampling cannot improve perception of the population-level distribution

## Interpretation {.tighter .smaller}

Ages caught and sampled in year 18 from one survey scenario:

>- $D_{sets} = 0.002, M_{lengths} = 500, M_{ages} = 10$

<dev class = "left">
```{r, fig.height = 4.8}

samp <- merge(main_sim$setdet, main_sim$samp, by = "set")
samp <- samp[sim == 1 & year == 18, ]
caught <- as.data.frame(table(samp$age))
caught <- data.frame(group = "Caught", age = caught$Var1, freq = caught$Freq,
                     prop = caught$Freq / sum(caught$Freq))
measured <- as.data.frame(table(samp$age[samp$measured]))
measured <- data.frame(group = "Sampled", age = measured$Var1, freq = measured$Freq,
                       prop = measured$Freq / sum(measured$Freq))
true <- data.frame(group = "True", age = sim$ages, freq = sim$I[, 1],
                   prop = sim$I[, 1] / sum(sim$I[, 1]))
d <- rbind(caught, measured, true)

plot_ly(data = d) %>% 
  add_lines(x = ~age, y = ~prop, color = ~group,
            colors = rev(viridis::viridis(3))) %>% 
  tight_layout(xaxis = list(title = "Age"),
               yaxis = list(title = "Proportion"),
               margin = list(r = 60))

```
</dev>

## Conclusions

- Increasing sub-sampling effort may be an inefficient means of improving population estimates
    - Especially problimatic if sub-sampling affects primary sampling effort

## Potential future directions

- Taylor to other species and assess sampling protocol
- Add a time component to assess trade-offs / efficiency
- Assess the effects of
    - Missing strata
    - Variable trawl area
- Use this as a platform to test spatial models
- Use as an operating model for an MSE
- Others?
